Sandbox Testing Latex

### 2019-06-25 _other/pandoc/fansample.tex
update pandoc instructions, more citation details.

\textcite{becker_human_1986} is a paper on Human Capital.

@@

For editing latex files in word.

@@

\subsection{Convert from back to Tex from Word}

>>>>

\textcite{becker_human_1986} is a paper on Human Capital. Early childhood health and economic circumstances could have lasting effects on adult socioeconomic outcomes \autocite{case_lasting_2005}.\footnote{"In this article, we develop a framework for analyzing the causal effects of interventions in the presence of latent factors that could affect outcomes, even in the absence of interventions" \autocite{conti_understanding_2010}.}

@@

For editing latex files in word to benefit from tracked changes.

@@

\subsection{Convert from Word from Tex}
